Improving the portuguese hyphenation rules

### 2023-07-13 article/article.tex
fix #9
fix #10

Another important matter to consider is ambiguities that might be created when
a word is partitioned during the hyphenation process. In English we should
avoid hyphenations such as re-cover, re-form, re-sign, the-rapist,
depart-mental and mans-laughter (in Portuguese, some examples are:
\emph{de-putada}, \emph{fede-ração}, \emph{acu-mula}, \emph{após-tolo},
\emph{cú-bico}). Hyphenations that might lead the reader to pronounce a word
incorrectly should also be prevented. That is the case of
\emph{considera-tion}, in Enslish (and \emph{pe-rigo} in Portuguese).

@@

    \item[Abbreviations, Acronyms, or Initialisms:] Whether for efficiency, 
	convenience, clarity or jargon, it is usual the usage of a shortening 
	version of a word or a phrase. 
	Abbreviation a way to shorten a word of phrase. Some examples in our
	Portuguese corpus are: 
	\emph{etc.}\footnote{Latin expression \emph{et cetera}, meaning 
	`and other similar things'.}, 
	\emph{Dr.}\footnote{\emph{doutor} (doctor, person with PhD title, but popularly used to designate an erudite individual)}, 
	\emph{Exmo.}\footnote{\emph{Excelentíssimo} (honourable)},
	\emph{cap.}\footnote{\emph{capítulo} (chapter)}, \emph{Univ.}\footnote{Universidade (university)}, 
	\emph{ed.}\footnote{\emph{edição} (edition)}, 
	\emph{s.n.}\footenote{sine nomine, Latin expression meaning `without a name', 
	mostly used in the context of publishing.}.
	Initialism consists of a set of initial 
	letters of words that form an shortened version. They are not always 
	understood by the set of hyphenation rules described in this work, 
	since they do not follow orthographic (or phonotactic) standards of 
	the language. In the corpus, it is possible to find some abbreviations, 
	such as \emph{SESC}\footnote{Serviço Social do Comércio}, 
	\emph{INSS}\footnote{\emph{Instituto Nacional do Seguro Social} (National Institute of Social Security)}, 
	\emph{PCdoB}\footnote{\emph{Partido Comunista do Brasil} (Communist Party of Brazil)},
	\emph{PM}\footnote{\emph{Polícia Militar} (military police)} and 
	\emph{UFRJ}\footnote{Universidade Federal do Rio de Janeiro}.
	Acronym is a type of abbreviation that shortens a phrase by combining
	the first letter (or letters) of each word, creating a new pronounceable word.
	Some example from the corpus are: 
	\emph{Anatel}\footnote{\emph{Agência Nacional de Telecomunicações} (National Telecommunications Agency)},
	\emph{Ovni}\footnote{\emph{Objeto voador não identificado} (unidentified flying object - UFO)},
	\emph{Sida}\footnote{\emph{Síndrome da Imunodeficiência Adquirida} (acquired immunodeficiency syndrome - AIDS)} (in Portugal) and
	\emph{Mercosul}\footnote{\emph{Mercado Comum do Sul} (Southern Common Market).}.
\end{description}

>>>>

Another important matter to consider is ambiguities that might be created when
a word is partitioned during the hyphenation process. In English we should
avoid hyphenations such as \emph{re-cover}, \emph{re-form}, \emph{re-sign}, \emph{the-rapist},
\emph{depart-mental} and \emph{mans-laughter} (in Portuguese, some examples are:
\emph{de-putada}, \emph{fede-ração}, \emph{acu-mula}, \emph{após-tolo},
\emph{cú-bico}). Hyphenations that might lead the reader to pronounce a word
incorrectly should also be prevented. That is the case of
\emph{considera-tion}, in Enslish (and \emph{pe-rigo} in Portuguese).

@@

    \item[Abbreviations, Acronyms, or Initialisms:] Whether for efficiency, 
	convenience, clarity or jargon, it is usual the usage of a shortening 
	version of a word or a phrase. 
	Abbreviation a way to shorten a word of phrase. Some examples in our
	Portuguese corpus are: 
	\emph{etc.}\footnote{Latin expression \emph{et cetera}, meaning 
	`and other similar things'.}, 
	\emph{Dr.}\footnote{\emph{doutor} (doctor, person with PhD title, but popularly used to designate an erudite individual)}, 
	\emph{Exmo.}\footnote{\emph{Excelentíssimo} (honourable)},
	\emph{cap.}\footnote{\emph{capítulo} (chapter)}, \emph{Univ.}\footnote{Universidade (university)}, 
	\emph{ed.}\footnote{\emph{edição} (edition)}, 
	\emph{s.n.}\footnote{sine nomine, Latin expression meaning `without a name', 
	mostly used in the context of publishing.}.
	Initialism consists of a set of initial 
	letters of words that form an shortened version. They are not always 
	understood by the set of hyphenation rules described in this work, 
	since they do not follow orthographic (or phonotactic) standards of 
	the language. In the corpus, it is possible to find some abbreviations, 
	such as \emph{SESC}\footnote{Serviço Social do Comércio}, 
	\emph{INSS}\footnote{\emph{Instituto Nacional do Seguro Social} (National Institute of Social Security)}, 
	\emph{PCdoB}\footnote{\emph{Partido Comunista do Brasil} (Communist Party of Brazil)},
	\emph{PM}\footnote{\emph{Polícia Militar} (military police)} and 
	\emph{UFRJ}\footnote{Universidade Federal do Rio de Janeiro}.
	Acronym is a type of abbreviation that shortens a phrase by combining
	the first letter (or letters) of each word, creating a new pronounceable word.
	Some example from the corpus are: 
	\emph{Anatel}\footnote{\emph{Agência Nacional de Telecomunicações} (National Telecommunications Agency)},
	\emph{Ovni}\footnote{\emph{Objeto voador não identificado} (unidentified flying object - UFO)},
	\emph{Sida}\footnote{\emph{Síndrome da Imunodeficiência Adquirida} (acquired immunodeficiency syndrome - AIDS)} (in Portugal) and
	\emph{Mercosul}\footnote{\emph{Mercado Comum do Sul} (Southern Common Market).}.
\end{description}
